### 2021-09-01 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
Intro additions and large tables

Recompression supercritical CO$_2$ Brayton cycles are promising cycle configurations offering higher efficiencies, compact design, and reduced turbomachinery cost while operating with non toxic working fluid. Higher efficiencies, in some simple recompression cycles reaching 50\% efficiency, allows for clean renewable and alternative energy sources to be competitive choices to coal powered steam Rankine cycles \cite{turchi_2013,wright_2009}. Various sCO$_2$ Brayton cycles have been modeled with the recompression cycle having the most efficiency advantages over other proposed cycle arrangements \cite{wang_2018,turchi_2012}.  Due to the benefits of sCO$_2$ Brayton cycles the United States Department of Energy is investigating these conversion cycles for use with heat sources including nuclear and solar \cite{doe_2012}. Utilizing complementary technologies, specifically solar concentrating power and lead-cooled fast reactors, can offset the drawbacks of each. Coupling these technologies into an interconnected cycle allows for consistent generation, independent of weather or time of day, and thermal storage for high dispatchability during high grid demand periods.

@@

Implementation of a combined solar and nuclear plant, modeled in a 2020 study from the School of Energy and Power Engineering in Jilin, China, shows a single recompression cycle layout with and emphasis on a cycle design's performance to varying solar irradiance and demonstration of feasibility with no demonstration of varied cycle arrangements \cite{wang_2020}.

@@

Black box heat exchangers are simplified heat exchangers which have no approach temperature or pinch point. These heat exchangers use an energy balance with mass flow inlet energy, heat input or output, and mass flow outlet energy. The energy balance equation used for all black box heat exchangers is Equation \ref{eq-black}.

@@

 Where $\dot{Q}_{HX}$ is the total heat transfer rate from the hot stream to the cold stream, $\dot{m}_{c}$ is the mass flow rate of the cold stream, $h_{out,c}$ is the enthalpy at the outlet of the cold side, and $h_{in,c}$ is the inlet of the cold side.
 The known heat transfer of the counter-flow heat exchanger can then solve for the enthalpy out of the hot stream, h$_{out,h}$. This is done with Equation \ref{enthalpy_h}.

@@

Knowing the state points on all inlets and outlets of the counter-flow heat exchanger allows for the heat exchanger performance metrics to be calculated. Performance metrics include effectiveness, capacitance ratio, UA, and NTU for heat exchangers. Effectiveness is the ratio of the actual heat transfer rate to the maximum heat transfer rate, or a perfect heat exchanger with no approach temperature. Assuming the approach temperature is on the high side, the maximum heat transfer rate, $\dot{Q}_max$ is found with the maximum enthalpy. Maximum enthalpy of the cold stream is found with correlations by setting the temperature to T$_{in,h}$ with same pressure on the cold outlet. Using the maximum enthalpy, $h_{max}$, the maximum heat transfer rate is calculated using Equation \ref{heattrans_max}.

>>>>

Recompression supercritical CO$_2$ Brayton cycles are promising cycle configurations offering higher efficiencies, compact design, and reduced turbomachinery cost while operating with non toxic working fluid. High efficiencies, in some simple recompression cycles reaching 50\% efficiency, allow for clean renewable and alternative energy sources to be competitive choices to coal powered steam Rankine cycles \cite{turchi_2013,wright_2009}. Various sCO$_2$ Brayton cycles have been modeled with the recompression cycle having the most efficiency advantages over other proposed cycle arrangements \cite{wang_2018,turchi_2012}.  Due to the benefits of sCO$_2$ Brayton cycles, the United States Department of Energy is investigating these conversion cycles for use with heat sources including nuclear and solar \cite{doe_2012}. Multiple project funding opportunities are established with the National Energy Technology Laboratory offering 144 million dollar reward for demonstration and performance verification of a sCO$_2$ Brayton cycle \cite{netl_2016} and the Office of Energy Efficiency \& Renewable Energy offering 2.6 million dollar reward in their Brayton Energy project for a integrated CSP receiver, TES, and power block in one sCO$_2$ Brayton system \cite{seto_2015}. Utilizing complementary technologies, specifically solar concentrating power and lead-cooled fast reactors, can offset the drawbacks of each. Coupling these technologies into an interconnected cycle allows for consistent generation, independent of weather or time of day, and thermal storage for high dispatchability during high grid demand periods.

@@

Various studies on complimentary solar-nuclear systems have been accomplished with several presented as follows. Monnerie et al. (2011), in search of an alternative to the typical fossil fuel-based process, reports on combining nuclear and solar energy in the same plant to produce hydrogen \cite{monnerie_2011}.  Extraction and production of fuels using complimentary solar-nuclear systems is additionally studied in the Curtis 2015 thesis from Massachusetts Institute of Technology where cycle configuration, performance, and development of shale oil extraction from kerogen deposits is reported \cite{curtis_2015}. Utilizing complimentary solar-nuclear cycles for production of hydrogen or shale oil with economical feasibility of the system discussed, in contrast to a fucus on electrical generation and storage in a sCO$_2$ Brayton recompression cycle, is not within the scope of the presented research in this paper. Implementation of a combined solar and nuclear plant, modeled in the Wang et al. (2020) shows a single sCO$_2$ Brayton recompression cycle layout with an emphasis on a cycle design's performance to varying solar irradiance and demonstration of feasibility \cite{wang_2020}.  This single cycle configuration has a dissimilar higher-temperature operating salt, KCl-MgCl$_2$, as the heat transfer fluid in the CSP with the small modular lead-cooled fast reactor's main purpose as a preheater to the CSP heat addition instead of being utilized as an TES charging alternative. Presented in this paper are the effects on cycle and heat storage efficiency of alternative heat addition locations while having the LFR serve a dual purpose of electrical generation and a suplementary CSP TES charging technique.

@@

Black box heat exchangers are simplified heat exchangers which have no approach temperature or pinch point and are modeled as a perfect heat transfer into or out of the cycle. These heat exchangers use an energy balance with mass flow inlet energy, heat input or output, and mass flow outlet energy. The energy balance equation used for all black box heat exchangers is Equation \ref{eq-black}.

@@

 Where $\dot{Q}_{HX}$ is the total heat transfer rate from the hot stream to the cold stream, $\dot{m}_{c}$ is the mass flow rate of the cold stream, $h_{out,c}$ is the enthalpy at the outlet of the cold side, and $h_{in,c}$ is the inlet of the cold side.
 The known heat transfer of the counter-flow heat exchanger can then solve for the enthalpy out of the hot stream, h$_{out,h}$. This is accomplished with Equation \ref{enthalpy_h}.

@@

Knowing the state points on all inlets and outlets of the counter-flow heat exchanger allows for the heat exchanger performance metrics to be calculated. Performance metrics include effectiveness, capacitance ratio, UA, and NTU for heat exchangers. Effectiveness is the ratio of the actual heat transfer rate to the maximum heat transfer rate, or a perfect heat exchanger with no approach temperature. Assuming the approach temperature is on the high side, the maximum heat transfer rate, $\dot{Q}_{max}$ is found with the maximum enthalpy. Maximum enthalpy of the cold stream is found with correlations by setting the temperature to T$_{in,h}$ with same pressure on the cold outlet. Using the maximum enthalpy, $h_{max}$, the maximum heat transfer rate is calculated using Equation \ref{heattrans_max}.
